---
title: "Hockey Model"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#library necessary package
library(tidyverse)

#read in data
shots<-read.csv("shots_2019.csv")

#take a look at data
head(shots)

```

Below, we will be selecting 7 columns from the data set for our logistic regression model. We will be predicting the likelihood of a goal based on:
1.) shooterTimeOnIce - the amount a time since the start of the shooter's shift up until the shot is taken
2.) arenaAdjustedShotDistance - distance from the net the shot is taken
3.) defendingTeamAverageTimeOnIce - the average current shift length of all players on the defending team when the shot is taken
4.) speedFromLastEvent - The distance between the shot location and the previous event's location divded by the number of seconds between them
5.) shotRush - Set to 1 if the shot was on a rush. (If the last event was in another zone and within 4 seconds) 0 if not
6.) shotRebound - Set to 1 if the shot is a rebound. (If the last event was a shot and within 3 seconds of this shot) 0 if not

```{r filter}

#filter data
shots1 <- shots %>% select(goal, shooterTimeOnIce, arenaAdjustedShotDistance, defendingTeamAverageTimeOnIce, speedFromLastEvent, shotRush, shotRebound)

#take a look again at filtered data
head(shots1)

```


```{r logistic regression}
#set binary data as factor data
shots1$shotRush <- as.factor(shots1$shotRush)
shots1$shotRebound <- as.factor(shots1$shotRebound)

#create model
mylogit <- glm(goal ~ shooterTimeOnIce + arenaAdjustedShotDistance + defendingTeamAverageTimeOnIce + speedFromLastEvent + shotRush + shotRebound, data = shots1, family = "binomial")

#model results -- any key take aways here?
summary(mylogit)
```
*.Rdata binary
*.RData binary
*.rda   binary
*.rdb   binary
*.rds   binary
*.Rd    text
*.Rdx   binary
*.Rmd	  text
*.R  	  text
*.Rproj text
*.[Rr]md   linguist-detectable
